---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TagR

<!-- badges: start -->
<!-- badges: end -->

TagR helps you work with TeamTV “tagged shots” exports for korfball. It provides:

- strict input validation for TeamTV shot exports (column names, types, and coding levels)
- quick quality checks (missingness patterns)
- shot location visualizations on a korfball half-field
- team descriptives tables + plots for coaching dashboards
- simple per-player analysis plots (binomial trends for distance, pressure, and shot count)
- a leg preference slider for comparing players at a glance

## Installation

You can install the development version of TagR from GitHub with:

``` r
# install.packages("pak")
pak::pak("EmmaDirk/TagR")
```

## Data format

Most TagR functions expect a TeamTV shot export with the same structure as the example dataset shipped with the package:

```{r}
library(TagR)

str(shots, 1)
```

## Input validation

TagR is strict on purpose: if TeamTV changes its export format or coding, TagR will error with an informative message.

```{r}
validate_teamtv_shots(shots)
```

If there are no problems, the validator returns invisibly (no output).

## Missingness patterns

A quick way to see missingness patterns and whether “onbekend” values are effectively treated as missing.

```{r}
p <- tagr_plot_missingness(shots)
p
```

You can also focus on one player (fuzzy match on `full_name`):

```{r}
p <- tagr_plot_missingness(shots, person = "Joost Dek")
p
```

## Shot location plots

TagR includes shot plotting functions that draw a korfball half-field (20 x 20 m) with the korf and the oval zone, then overlays shot locations.

```{r, eval=FALSE}
# Example: result-colored plot (GOAL vs MISS) with filters
p <- tagr_plot_shots_result(
  shots,
  player = "11",
  filter_type = c("LONG", "SHORT"),
  filter_pressure = c("NONE", "MEDIUM"),
  filter_leg = c("LEFT", "RIGHT")
)
p
```

Notes:
- shots are shifted to the correct coordinate origin used by the TeamTV export
- shots outside the pitch are clamped to the pitch border
- the pitch styling is fixed and not exposed as user options

## Team descriptives (tables + plots)

Compute goal percentages by key categories (pressure, distance band, shot type, shot count band, leg). Returns plain data.frames so they are easy to inspect and test.

```{r}
tabs <- tagr_team_overview_tables(shots)

names(tabs)
tabs$pressure
tabs$type
```

Plot one attribute as a quick bar chart:

```{r}
tagr_team_overview_plot(shots, attribute = "pressure")
tagr_team_overview_plot(shots, attribute = "distance")
```

Filter to a single player (fuzzy match on name or exact match on number):

```{r}
tagr_team_overview_plot(shots, attribute = "type", player = "11")
```

## Player analysis (binomial trend plots)

TagR provides simple binomial model visualizations to show how scoring probability changes with:
- distance (capped at 10 m)
- pressure (NONE < MEDIUM < HIGH)
- shot count band (1, 2, 3, 4+)

Player plots optionally include the team line/points for comparison, and you can restrict to LONG/SHORT only.

```{r}
tagr_plot_prob_by_distance(shots)
tagr_plot_prob_by_distance(shots, player = "11", long_short_only = TRUE)

tagr_plot_prob_by_pressure(shots, player = "Joost Dek")
tagr_plot_prob_by_shot_count(shots, player = "11")
```

## Leg preference slider

A compact visualization that places all players on a left-to-right “leg preference” slider. It uses only SHORT, LONG, and FREE-BALL shots and combines volume and success per leg (BOTH pulls toward the center). The y-axis shows number of shots, and each dot is labeled with the player name/number.

```{r}
tagr_plot_leg_preference_slider(shots)
```


