---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TagR

<!-- badges: start -->
<!-- badges: end -->

TagR helps you work with TeamTV “tagged shots” exports for korfball. It provides:

- quick quality checks (missingness patterns)
- shot location visualizations on a korfball half-field
- team descriptives tables + plots for coaching dashboards
- simple per-player analysis plots (binomial trends for distance, pressure, and shot count)
- a leg preference slider for comparing players at a glance

## Installation

You can install the development version of TagR from GitHub with:

``` r
# install.packages("pak")
pak::pak("EmmaDirk/TagR")
```

## Data format

Most TagR functions expect a TeamTV shot export with the same structure as the example dataset shipped with the package:

```{r}
library(TagR)

str(shots, 1)
```

## Missingness patterns

A quick way to see what information you do, and do not have.

```{r}
p <- tagr_plot_missingness(shots)
p
```

## Shot location plots

TagR includes visualisations of shot location, filtered in various ways. 
```{r}
# Example: result-colored plot (GOAL vs MISS) 
p <- TagR::tagr_plot_shots_result(TagR::shots)
p
```

Like many other functions in this package, plotting functions accept an optional `player` argument (fuzzy match on name or exact match on number). 

```{r}
# Example: plot shots for player number 11 only
p <- TagR::tagr_plot_shots_pressure(TagR::shots, player = "11")
p
```

## Team descriptives (tables + plots)

Compute goal percentages by key categories (pressure, distance band, shot type, shot count band, leg). Returns plain data.frames so they are easy to inspect and test.

```{r}
tabs <- tagr_team_overview_tables(shots)

names(tabs)
tabs$pressure
tabs$type
```

Plot one attribute as a quick bar chart:

```{r}
tagr_team_overview_plot(shots, attribute = "pressure")
tagr_team_overview_plot(shots, attribute = "distance")
```

Filter to a single player (fuzzy match on name or exact match on number):

```{r}
tagr_team_overview_plot(shots, attribute = "type", player = "11")
```

## Player analysis (binomial trend plots)

TagR provides simple visualizations to show how scoring probability changes with:

- distance (capped at 10 m)
- pressure (NONE < MEDIUM < HIGH)
- shot count band (1, 2, 3, 4+)

Player plots optionally include the team line/points for comparison, and you can restrict to LONG/SHORT shots only, including only shots from open play. 

```{r}
tagr_plot_prob_by_distance(shots)
tagr_plot_prob_by_distance(shots, player = "11", long_short_only = TRUE)

tagr_plot_prob_by_pressure(shots, player = "Joost Dek")
tagr_plot_prob_by_shot_count(shots, player = "11")
```

## Leg preference slider

A compact visualization that places all players on a left-to-right “leg preference” slider. It uses only SHORT, LONG, and FREE-BALL shots and combines volume and success per leg. The y-axis shows number of shots, and each dot is labeled with the player name/number.

```{r}
tagr_plot_leg_preference_slider(shots)
```


