---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width = 12,
  fig.height = 7,
  dpi = 200,
  fig.retina = 2
)
```

# TagR

<!-- badges: start -->
<!-- badges: end -->

TagR helps you work with “tagged shots” from the popular TeamTV analysis platform, mainly used in korfball. It includes: 

- Functions to tell you what information you miss.
- Various visualisations of tagged shots. 
- Dashboards to compare and analyse teams and individual players at a glance.

## Installation

You can install the development version of TagR from GitHub with:

``` r
# install.packages("pak")
pak::pak("EmmaDirk/TagR")
```

## Data format

TagR functions expect a TeamTV shot export with the same structure as the example dataset shipped with the package:

```{r}
library(TagR)

str(shots, 1)
```

## Missingness patterns

A quick way to see what information you have, and what information you have not yet recorded. 

```{r}
# example: plot missingness pattern for all shots
p <- tagr_plot_missingness(shots)
p
```

## Shot visualisations by location

TagR includes visualisations of shot location, where various attributes of the shots can be mapped to colour.
```{r}
# example: result-colored plot (GOAL vs MISS) 
p <- tagr_heatmap(shots, colour_by = "result")
p
```

Like many other functions in this package, plotting functions accept an optional `player` argument (fuzzy match on name or exact match on number). 

```{r}
# example: plot shots for player number 11 only
p <- tagr_heatmap(shots, colour_by = "result", player = "11")
p
```

Included shots can also be filtered by `type` (e.g., exclude freeballs), `result` (i.e. goal or miss), `pressure` level and `leg`. 

```{r}
# example: plot right legged shots for player number 11 only
p <- tagr_heatmap(shots, colour_by = "result", player = "11", filter = list(leg = "RIGHT"))
p
```

## Team dashboards

TagR provides quick overviews of team shooting performance across various attributes, including `pressure`, `distance`, shot `type`, `leg`, and `shot count band`. Ideal for coaches to get a quick sense of team performance and identify areas for improvement, or identify threats when preparing for upcoming opponents.

```{r}
# example: team overview dashboard
p <- tagr_team_dashboad(shots)
p
```

## Player dashboards

Or zoom in on individual players to see their shooting performance across various attributes, compared to the team average.

```{r}
# example: player overview dashboard for player number 10
p <- tagr_player_dashboard(shots, player = "17")
p
```

## Player analysis 

TagR provides simple visualizations to show how scoring probability changes with:

- `distance` (capped at 10 m)
- `pressure` (NONE < MEDIUM < HIGH)
- `shot count band` (1, 2, 3, 4+)

This can provide coaches with a simple way to view if players are struggling under pressure, or from longer distances. 

```{r}
# example: plot scoring probability by pressure for player number 10
p <- tagr_shot_analysis(shots, player = "10", feature = "pressure", add_team = TRUE)
p
```

where `feature` can also be `"distance"` or `"shot_count_band"`. Multiple players can be added by passing a vector to the `player` argument:

```{r}
# example: plot scoring probability by distance for player number 10
p <- tagr_shot_analysis(shots, player = c("10", "17"), feature = "distance", add_team = TRUE)
p
```

